Effect of quality-adjusted production function inputs

### 2015-06-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using getData instead of model$data.

<<Fitted_and_Residuals>>=
fittedAndResidData <- function(model){
  df <- data.frame(select(model$data, Year))
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(model)[c(1:length(df$Year))]
  df$Residuals <- resid(model)[c(1:length(df$Year))]
  return(df)  
}

temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
  df <- fittedAndResidData(model)
  f <- model$formula
  response <- summands(f, right = FALSE)
  df[[response]] <- model$data[[response]] # Add iGDP to the data frame
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

@@

  f <- model$formula
  denom <- summands(f, n=length(summands(f))) # time variable
  nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
  df <- model$data[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)

@@

lag.to.use <- 1 # years
temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), 
                        f = function(model, id, lag=lag.to.use, pad="tail"){
  df <- dynamicSR(model, id=id, lag=lag, pad=pad)
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  df$Year <- model$data[["Year"]]
  return(df)  
}) %>% do.call(plyr::rbind.fill, .)

>>>>

<<Fitted_and_Residuals>>=
fittedAndResidData <- function(model){
  df <- data.frame(select(getData(model), Year))
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(model)[c(1:length(df$Year))]
  df$Residuals <- resid(model)[c(1:length(df$Year))]
  return(df)  
}

temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
  df <- fittedAndResidData(model)
  f <- model$formula
  response <- summands(f, right = FALSE)
  df[[response]] <- getData(model)[[response]] # Add iGDP to the data frame
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

@@

  f <- model$formula
  denom <- summands(f, n=length(summands(f))) # time variable
  nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
  df <- getData(model)[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)

@@

lag.to.use <- 1 # years
temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), 
                        f = function(model, id, lag=lag.to.use, pad="tail"){
  df <- dynamicSR(model, id=id, lag=lag, pad=pad)
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  df$Year <- getData(model)[["Year"]]
  return(df)  
}) %>% do.call(plyr::rbind.fill, .)
